Crossing Origins by Crossing Formats

### 2012-11-30 main.tex
a few global edits

By crossing origins we mean being able to request and access content
which is normally restricted under the same-origin policy. 
Recall that SOP only allows two documents accessing each others'
content and resources if they share the origin. Similarly,
a document can only directly communicate with the server from which it originated. 
This is not to be confused with \emph{cross-origin resource sharing} (CORS)~\cite{w3-cors}, which is an 
intentional relaxation of SOP.

@@

Not all elements are as carefully restricted from information leaks as images. 
Scripts loaded across origins become part of the document and inherit the 
origin of the including document, which allows the script to communicate with the 
server from which the \emph{document} originated. Such scripts are also able to interact 
with the document, e.g. by adding nodes, which in turn require new content to be 
requested. Since these requests are not restricted by SOP, this creates a side 
channel that permits cross-origin information leakage. At the same time, the including document
is prevented from inspecting the source of the script and can only observe the public 
side-effects that the script produce as it is executed.

@@

Coercing content to be interpreted
as a different type can be accommodated in the context of the web. 
If the content is loaded using an \emph{image} tag it will be interpreted 
as an image, if a \emph{script} tag is used it will be interpreted as a script. Some 
tags even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues.
\todo{explain the issues and cite Barthe et al.}

@@

\subsubsection{The target}
There are two methods for a PDF to communicate with the server it originated from, 
that allow it to read the response; from JavaScript using XML external entities 
or from an embedded flash file.

@@

\paragraph{Embedded Flash}
Cross-origin communication in Flash is restricted by the same-origin policy,
but also support cross-origin communication via Cross-Origin Resource Sharing 
(CORS). Using CORS, a web server can relax SOP to allow access to specified content.
As mentioned, the embedded Flash file inherits the origin of the document.
However, this is not a restriction, since an attacker can set a cross-origin policy 
that allow the request. This allows for a two way communication that is not 
visible to the victim.

the minimal malformed structure that is required for Adobe Reader to consider ita PDF.

@@

As for the PDF file format, the underlying design decisions has led to the 
current parsing being very relaxed, even with respect to the specification. 
Making the parsing more strict and enforcing many of the specified requirements 
will reduce the attack surface. It is, however, not a complete 
mitigation approach. Since the PDF format is a container format it is designed to 
embed syntax from other files. Even when parsing strictly according to 
the specification, it is a simple task to create a PDF-based polyglot.

>>>>

By crossing origins we mean being able to request and access content
which is normally restricted under the same-origin policy. 
Recall that SOP only allows two documents accessing each others'
content and resources if they share the origin. Similarly,
a document can only directly communicate with the server from which it originates. 
This is not to be confused with \emph{cross-origin resource sharing} (CORS)~\cite{w3-cors}, which is an 
intentional relaxation of SOP.

@@

Not all elements are as carefully restricted from information leaks as images. 
Scripts loaded across origins become part of the document and inherit the 
origin of the including document, which allows the script to communicate with the 
server from which the \emph{document} originates. Such scripts are also able to interact 
with the document, e.g. by adding nodes, which in turn require new content to be 
requested. Since these requests are not restricted by SOP, this creates a side 
channel that permits cross-origin information leakage. At the same time, the including document
is prevented from inspecting the source of the script and can only observe the public 
side-effects that the script produce as it is executed.

@@

Coercing content to be interpreted
as a different type can be accommodated in the context of the web. 
If the content is loaded using an \emph{image} tag it will be interpreted 
as an image, if a \emph{script} tag is used it will be interpreted as a script. Some 
tags even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues.
\todo{explain the issues and cite Barth et al.~\cite{Barth+:SP09}}

@@

\subsubsection{The target}
There are two methods for a PDF file to communicate with the server it originates from, 
both allowing it to read the response: from JavaScript using XML external entities 
and from an embedded flash file.

@@

\paragraph{Embedded Flash}
Cross-origin communication in Flash is restricted by the same-origin policy,
but also support cross-origin communication via  
CORS. Using CORS, a web server can relax SOP to allow access to specified content.
As mentioned, the embedded Flash file inherits the origin of the document.
However, this is not a restriction, since an attacker can set a cross-origin policy 
that allow the request. This allows for a two way communication that is not 
visible to the victim.

\subsection{Syntax injection}
the minimal malformed structure that is required for Adobe Reader to consider ita PDF.

@@

As for the PDF file format, the underlying design decisions have led to the 
current parsing being very relaxed, even with respect to the specification. 
Making the parsing more strict and enforcing many of the specified requirements 
will reduce the attack surface. It is, however, not sufficient for complete 
mitigation because the PDF format is a container format it is designed to 
embed syntax from other files. Even when parsing strictly according to 
the specification, it is a simple task to create a PDF-based polyglot.
